---
title: "ASSIGNMENT6_WANKELMAN"
output: pdf_document
date: "2024-03-04"
---
1: In a few paragraphs, explain when and why dictionaries successfully measure that which they attempt to measure, when they do not, and the possible risks of analyzing text with dictionaries.
* Things to consider: 
*** Can a human-defined set of terms accurately measure sentiment or other topics?
*** Are dictionaries good because they have low compute requirements?
*** Have you heard or seen dictionaries or dictionary methods applied today?

Dictionaries in text analysis are essential in quantifying constructs such as sentiment, stereotypes, or different emotional states from textual data. They operate on a relatively simple premise: a predefined list of words is associated with specific sentiments or topics, and the presence of these words in a text is used to infer the text's overall sentiment or thematic content. This approach has several advantages, including low computational requirements compared to more advanced natural language processing (NLP) techniques, making dictionaries particularly appealing for researchers with limited resources or needing quick analyses.

However, the effectiveness of dictionaries in accurately measuring what they are supposed to measure varies significantly depending on the context and how the dictionary is constructed. For instance, when dictionaries are well-crafted with extensive validation from multiple professional sources and other measures, they can achieve higher levels of coverage and reliability, as illustrated in the development of stereotype content dictionaries using Wordnet and word embeddings. These dictionaries capture the most relevant responses, indicating their success in measuring the intended constructs.

Yet, dictionaries have limitations. Their reliance on predefined word lists means they can miss nuances in language use, such as sarcasm, negation, or the evolving meanings of words over time. Additionally, words may have different meanings in different contexts, which a straightforward dictionary approach must accurately capture. For example, "cold" can refer to temperature, a personality trait, or an illness, which would be relevant in different analytical contexts. The static nature of dictionaries also means they may adapt well to new domains or slang with manual updates, posing challenges for analyzing texts from dynamic or evolving language environments, such as social media.

Analyzing text with dictionaries carries risks, including the potential for over-representing particular sentiments or themes due to the dictionary's limitations in capturing language complexity. If the dictionary's coverage or the specificity of the context needs to be adequately considered, results can be misinterpreted. Furthermore, reliance on dictionaries might discourage deeper engagement with data that could reveal more nuanced insights, particularly in rich, open-ended text responses.

Despite these challenges, dictionaries remain valuable in text analysis due to their ease of use, low computational demand, and the potential for high validity in specific contexts when carefully constructed and validated. The continued application and development of dictionaries, especially with advancements in automated dictionary creation and validation methods, underscore their relevance in text analysis. Yet, researchers must be mindful of their limitations, complementing dictionary-based approaches with other methods to ensure a comprehensive understanding of textual data.


Loughran, T., & McDonald, B. (2011). When Is a Liability Not a Liability? Textual Analysis, Dictionaries, and 10-Ks. https://doi.org/10.1111/j.1540-6261.2010.01625.x

Kim, H. (2022). Sentiment Analysis: Limits and Progress of the Syuzhet Package and Its Lexicons. Volume 16(Number 2). https://orcid.org/0000-0002-2049-7531

Nicolas G, Bai X, Fiske ST. Comprehensive stereotype content dictionaries using a semi-automated method. Eur J Soc Psychol. 2021; 51: 178–196. https://doi.org/10.1002/ejsp.2724



```{r}
# Read in some data to analyze. In this case we reuse homework data
# but hopefully you are starting to look at the final project data and may use that.

# Lets look at the qdapDictionaries documentation (An important step often ignored)
# https://cran.r-project.org/web/packages/qdapDictionaries/qdapDictionaries.pdf

# Next we have to figure out what a dictionary even is
# https://www.google.com/search?q=quanteda+dictionary
# https://quanteda.io/reference/dictionary.html
```

```{r}
#Checking to ensure pdftools is updated
install.packages("pdftools")
```

```{r}
# Load Libaraies
library(quanteda)
library (qdapDictionaries)
library(quanteda.textstats)
library(httr)
library(httr2)
library(jsonlite)
library(ndjson)
library(rjson)
library(dplyr)
library(tidytext)
library(wordcloud2)
library(readtext)
library(pdftools)
library(tm)
library(jsonview)
library(ggplot2)
library(readr)
library(tidyr)
```


############################## ############################## 
#### qdapDictionary Approach
qdap is another set of packages that can be used together but we will be stickin with trusty Quanteda.
############################## ############################## 

```{r}
# Select the correct qdap dictionary
data(key.pol)
#Check out what is in key.pol
class(key.pol)
key.pol

```

```{r}
# key.pol is a data table and we saw that we need a dictionary format
# The easiest way is to convert this table into a list

# Check what are the possible values in key.pol
unique(key.pol$y)
# Just 1 for positive and -1 for negative

```

##########################
#### Convert to a list
##########################
```{r}
#Create a seperate list of positive and negative values for column x
key_pol_list = list(
  positive=key.pol[ which(y == 1), ]$x,
  negative=key.pol[ which(y == -1), ]$x
)

```


####################
# Running into errors with downloaded PDFs, Going have to manually inspect each document
####################

### How is the US Pricing Carbon PDF
```{r}
#Inspect each PDF to ensure they can be correctly read.  From previous code we know How can we price carbon should be recognized. Starting with this doc
how_is_the_us_pricing = pdf_text("/Users/jcw81/Desktop/JHU/Semester 2/Text to Data/Module 6/Carbon_Article/How Is the US Pricing Carbon? How Could We Price Carbon?.pdf")

```


```{r}
# Print the text of the tenth page to verify loaded the PDF
cat(how_is_the_us_pricing[10]) 

#https://stackoverflow.com/questions/39630212/pdftools-package-in-r-error-invalid-font-weight
```

```{r}
# Another method I discovered for verifying the successful loading of the PDF document involves loading and examining portions of specific pages I wanted to test.
# Print first 200 characters of first 15 pages with separators
for (i in 1:15) {
  cat(substr(how_is_the_us_pricing[i], 1, 200), "\n---\n")
}

#https://www.rdocumentation.org/packages/openintro/versions/2.4.0/topics/loop
#https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/seq
#https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/substr
#https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/cat
#https://support.sas.com/resources/papers/proceedings/proceedings/sugi25/25/cc/25p088.pdf
```

```{r}
# create the corpus
how_is_the_us_pricing_sentiment = corpus(how_is_the_us_pricing)
how_is_the_us_pricing_sentiment
```

```{r}
?tokens
```

```{r}
# Tokenize the PDF document
how_is_the_us_pricing_tokens = tokens(how_is_the_us_pricing_sentiment, 
                                      remove_punct = TRUE, 
                                      remove_numbers = TRUE, 
                                      remove_symbols = TRUE) %>% 
                               tokens_tolower()              

# https://tutorials.quanteda.io/advanced-operations/targeted-dictionary-analysis/
```

```{r}
# Overview of how PDF Document was Tokenized
summary(how_is_the_us_pricing_sentiment)
```

############################## ############################## 
# SentimentAnalysis Approach
https://cran.r-project.org/web/packages/SentimentAnalysis/vignettes/SentimentAnalysis.html
############################## ##############################
```{r}
#Load required library
library(SentimentAnalysis)
```

####
# Get the dictionary
####

```{r}
# Check to see datasets available in the qdapDictionaries package
data(package = "qdapDictionaries")

```


```{r}
# Accessing the dictionaries from qdapDictionaries package
data(DictionaryHE)
data(DictionaryLM)
DictionaryHE
# Looks like it is close to the correct format
class(DictionaryHE)
# So close, its a list. Close enough though.
```

####
# Apply sentiment dictionary
####
```{r}
#Create a document feature matrix (dfm). Trying to quantify sentiment in texts using DictionaryHE
sentiment_dict_result_how_is_us_pricing = dfm(how_is_the_us_pricing_sentiment, 
   dictionary=dictionary(DictionaryHE))
sentiment_dict_result_how_is_us_pricing

class(sentiment_dict_result_how_is_us_pricing)
```
```{r}
# Convert it to a data frame
sentiment_dict_result_how_is_us_pricing_he = convert(sentiment_dict_result_how_is_us_pricing, to = "data.frame")

# Summarize the sentiment counts
how_is_us_pricing_df_summary_he = sentiment_dict_result_how_is_us_pricing_he %>%
  summarise(
    Positive = sum(positive),
    Negative = sum(negative)
  ) %>%
  pivot_longer(
    cols = c(Positive, Negative),
    names_to = "Sentiment",
    values_to = "Count"
  )
```


```{r}
# Now, use ggplot2 to create a bar plot of sentiment counts
ggplot(how_is_us_pricing_df_summary_he, aes(x = Sentiment, y = Count, fill = Sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "Sentiment Analysis using DictionaryHE",
    x = "Sentiment",
    y = "Count"
  )
```


```{r}
#Create a document feature matrix (dfm). Trying to quantify sentiment in texts using DictionaryHE
dfm(how_is_the_us_pricing_sentiment, 
   dictionary=dictionary(DictionaryLM))

#The LM analysis is showing 0 potential negative with 7 positive and 10 uncertain
```

```{r}
# Convert it to a data frame
sentiment_dict_result_how_is_us_pricing_lm = convert(dfm(how_is_the_us_pricing_sentiment, dictionary=dictionary(DictionaryLM)), to = "data.frame")

# Summarize the sentiment counts
how_is_us_pricing_df_summary_lm = sentiment_dict_result_how_is_us_pricing_lm %>%
  summarise(
    Positive = sum(positive),
    Negative = sum(negative)
  ) %>%
  pivot_longer(
    cols = c(Positive, Negative),
    names_to = "Sentiment",
    values_to = "Count"
  )
```


```{r}
ggplot(how_is_us_pricing_df_summary_lm, aes(x = Sentiment, y = Count, fill = Sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Sentiment Analysis Summary",
       x = "Sentiment Type",
       y = "Count",
       fill = "Sentiment")
```
#### Question 2: Describe the results on your corpus. Do you find the results to be accurate? Why or why not?
The sentiment analysis conducted on the how_is_the_us_pricing corpus with DictionaryHE and DictionaryLM has yielded what I believe to be insightful results. The analysis, indicates a predominant presence of positive sentiment within the corpus. The first graph, derived using DictionaryHE, shows a notably higher count of positive sentiments in comparison to negative ones. The second graph, derived using DictionaryLM demonstrates a similar trend, albeit with a marginally increased count of negative sentiments. I would infer that these results suggest that the corpus is characterized by a more positive than negative tone. The disparity between the positive and negative sentiment counts could reflect the corpus's subject matter or the sentiment expression style inherent to the texts analyzed. These findings can play a pivotal role in understanding the overall sentiment trend in the analyzed texts.



####
# Count the Words from the Dictionary I made specifically for Carbon pricing
####
```{r}
#Load custom dictionary
carbon_dictionary = read_csv("~/Desktop/JHU/Semester 2/Text to Data/Module 6/carbon_pricing_terms2.csv", 
                             col_types = cols(Term = col_character())) # Used to remove a warning

class(carbon_dictionary)

```

```{r}
# The column 'Term' contains desired terms
terms_dict = dictionary(list(
  x = carbon_dictionary$Term %>% 
        tolower() %>%  # Convert terms to lowercase
        unique()       # Remove duplicate terms
))

terms_dict
```

```{r}
# Remove stopwords from the tokens
how_is_the_us_pricing_tokens_no_stopwords = tokens_remove(how_is_the_us_pricing_tokens, stopwords("en"), padding = FALSE)

```


```{r}
# Apply the dictionary 
how_is_the_us_pricing_keypol = tokens_lookup(how_is_the_us_pricing_tokens_no_stopwords, dictionary = terms_dict, exclusive = FALSE)

```


```{r}
# Create a DFM 
dfm_how_is_the_us_pricing_sentiment = dfm(how_is_the_us_pricing_keypol)

```


```{r}
# inspect the DFM 
dim(dfm_how_is_the_us_pricing_sentiment)

```

```{r}
# Remove the 'x' feature from the DFM if not it will occur the most times 
dfm_how_is_the_us_pricing_sentiment = dfm_remove(dfm_how_is_the_us_pricing_sentiment, "x")
```


```{r}
# Calculate term frequencies
term_counts_how_is_the_us_pricing_sentiment = textstat_frequency(dfm_how_is_the_us_pricing_sentiment)

# Print the term frequency results
print(term_counts_how_is_the_us_pricing_sentiment)
```

```{r}
# Graph frequency of words with bar chart
# Top 20 terms by frequency
top_terms = head(term_counts_how_is_the_us_pricing_sentiment, 20)

# Graph a bar chart with frequency of top 20 words
ggplot(top_terms, aes(x=reorder(feature, -frequency), y=frequency, fill=feature)) +
  geom_bar(stat="identity") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(y = "Frequency", 
       x = "", 
       title = "Top 20 Terms in US Pricing Sentiment Analysis", 
       fill = "Term") +
  guides(fill=FALSE) # Remove the legend
 

#https://cbail.github.io/SICSS_Dictionary-Based_Text_Analysis.html
#Data Viz Fall Semester
```


# Reaching For 2030: Climate and Energy Policy Priorities
```{r}
# Load PDF doc.  
climate_energy_policy_priorities = pdf_text("/Users/jcw81/Desktop/JHU/Semester 2/Text to Data/Module 6/Carbon_Article/reaching-for-2030-climate-and-energy-policy-priorities.pdf")
cat(future_us_carbon_pricing[10])

```

```{r}
# Print first 200 characters of first 15 pages
for (i in 1:10) {
  cat(substr(climate_energy_policy_priorities[i], 1, 200), "\n---\n")
}

```

```{r}
#Create corpus
climate_energy_policy_priorities_sentiment = corpus(climate_energy_policy_priorities)
climate_energy_policy_priorities_sentiment
class(climate_energy_policy_priorities_sentiment)
```

```{r}
#Tokenize corpus
climate_energy_policy_priorities_tokens = tokens(climate_energy_policy_priorities_sentiment, 
                                      remove_punct = TRUE, 
                                      remove_numbers = TRUE, 
                                      remove_symbols = TRUE) %>% 
                               tokens_tolower()  


# https://tutorials.quanteda.io/advanced-operations/targeted-dictionary-analysis/

```


```{r}
#Check tokens
summary(climate_energy_policy_priorities_sentiment)
```


############################## ############################## 
# SentimentAnalysis Approach
https://cran.r-project.org/web/packages/SentimentAnalysis/vignettes/SentimentAnalysis.html
############################## ##############################

```{r}
#Load required library
library(SentimentAnalysis)
```

```{r}
#Get the dictionary
data(DictionaryHE)
data(DictionaryLM)
DictionaryHE

class(DictionaryHE)

```

```{r}
# Apply sentiment dictionary HE
sentiment_dict_result_climate_energy_policy_priorities = dfm(climate_energy_policy_priorities_sentiment, 
   dictionary=dictionary(DictionaryHE))
sentiment_dict_result_climate_energy_policy_priorities
```

```{r}
# Apply sentiment dictionary LM
dfm(climate_energy_policy_priorities_sentiment, 
   dictionary=dictionary(DictionaryLM))

```

####
# Count the Words from the Dictionary I made specifically for Carbon pricing
####
```{r}
#Load custom dictionary
carbon_dictionary = read_csv("~/Desktop/JHU/Semester 2/Text to Data/Module 6/carbon_pricing_terms2.csv", 
                             col_types = cols(Term = col_character())) # Used to remove a warning

class(carbon_dictionary)

```

```{r}
# The column 'Term' contains desired terms
terms_dict = dictionary(list(
  x = carbon_dictionary$Term %>% 
        tolower() %>%  # Convert terms to lowercase
        unique()       # Remove duplicate terms
))

terms_dict
```


```{r}
# Remove stopwords from the tokens
climate_energy_policy_priorities_no_stopwords = tokens_remove(climate_energy_policy_priorities_tokens, stopwords("en"), padding = FALSE)

```

```{r}
# Apply the dictionary via tokens_lookup to match and aggregate tokens according to the dictionary entries
climate_energy_policy_priorities_keypol = tokens_lookup(climate_energy_policy_priorities_no_stopwords, dictionary = terms_dict, exclusive = FALSE)

```


```{r}
# Create a DFM from the matched tokens
dfm_climate_energy_policy_priorities_sentiment = dfm(climate_energy_policy_priorities_keypol)

```


```{r}
# Directly inspect the DFM without reapplying the dictionary
dim(dfm_climate_energy_policy_priorities_sentiment)

```

```{r}
# Remove the 'x' feature from the DFM
dfm_climate_energy_policy_priorities_sentiment = dfm_remove(dfm_climate_energy_policy_priorities_sentiment, "x")
```


```{r}
# Calculate term frequencies
term_counts_climate_energy_policy_priorities_sentiment = textstat_frequency(dfm_climate_energy_policy_priorities_sentiment)

# Print the term frequency results
print(term_counts_climate_energy_policy_priorities_sentiment)
```



```{r}
# Graph a bar chart with frequency of words
# Top 20 terms by frequency
top_terms = head(term_counts_climate_energy_policy_priorities_sentiment, 20)

# Graph a bar chart with frequency of top 20 words
ggplot(top_terms, aes(x=reorder(feature, -frequency), y=frequency, fill=feature)) +
  geom_bar(stat="identity") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(y = "Frequency", 
       x = "", 
       title = "Top 20 Terms in US Pricing Sentiment Analysis", 
       fill = "Term") +
  guides(fill=FALSE) # Remove the legend
 

#https://cbail.github.io/SICSS_Dictionary-Based_Text_Analysis.html
#Data Viz Fall Semester
```


#####################
# Prepare Carbon  data
######################
Read in data,Preferably start working on data you collected for your project

```{r}
# I removed a document to reduce the PDF error: Invaid Font Weight. This was a process that took a lot of work and after going through each PDF file and trying to visualize them, I decided circle back an attempt doing all the PDFs at once.


#Load Dataset folder
carbon_cases_path = "/Users/jcw81/Desktop/JHU/Semester 2/Text to Data/Module 6/Carbon_Article"

carbon_cases_pdfs = readtext(paste0(carbon_cases_path, "/*.pdf"),
                     encoding = "ISO-8859-1")

# Check the structure of the PDF documents
str(carbon_cases_pdfs)

#Quantitative Analysis of Textual Data. Importing Data from Multiple Files. Retrieved February 12, 2024, from https://tutorials.quanteda.io/import-data/multiple-files/

# I removed a document to reduce the PDF error: Invaid Font Weight
```

```{r}
# Create a corpus from the PDF documents
carbon_corpus = corpus(carbon_cases_pdfs$text)

# Check the structure of corpus
print(carbon_corpus)
summary(carbon_corpus)

#Quanteda Tutorials. Corpus. Retrieved February 12, 2024, from https://tutorials.quanteda.io/basic-operations/corpus/corpus/
```

```{r}
?tokens
```

```{r}
# Tokenize the PDFs corpus
tokens_corpus_cases = tokens(carbon_corpus)
```

```{r}
#Remove all punctuation from PDF corpus.
clean_tokens_cases = tokens(tokens_corpus_cases,
                        remove_punct = TRUE,
                        remove_numbers = TRUE,
                        remove_symbols = TRUE,
                        remove_url = TRUE,
                        remove_separators = TRUE,
                        split_hyphens = TRUE)

clean_tokens_cases
clean_tokens_cases %>% dfm()

#Quanteda Team. Tokens. quanteda. Retrieved February 12, 2024, from https://quanteda.io/reference/tokens.html
```

```{r}
#Applying stopwords to PDF documents
#https://stopwords.quanteda.io/

stopwords::stopwords_getsources()
stopwords::stopwords_getlanguages("snowball")
?stopwords::stopwords
stopwords::stopwords(source = "snowball", language = 'en')
stopwords::stopwords(source = "nltk", language = 'en')

class(stopwords::stopwords(source = "nltk", language = 'en'))


#Butkevics, Janis. February 13, 2024. TAD Mod 3 [Video]. AS 470.643.81 SP24. Johns Hopkins University. https://livejohnshopkins.sharepoint.com/
```

```{r}
#Drop stopwords.
clean_tokens_cases %>% 
  tokens_remove(pattern = stopwords::stopwords(source = "nltk", language = 'en')) %>%
  dfm() %>%
  textstat_frequency(n=200)

#Quanteda Initiative. Stopwords. Retrieved February 14, 2024, from https://stopwords.quanteda.io/
```

```{r}
clean_tokens_cases %>%
  tokens(tokens_corpus_cases,
         remove_punct = TRUE,
         remove_url = TRUE,
         remove_separators = TRUE,
         split_hyphens = TRUE) %>%
  tokens_remove(pattern = stopwords::stopwords(source = "snowball", language = 'en')) %>%
  dfm()

#Butkevics, Janis. February 13, 2024. TAD Mod 3 [Video]. AS 470.643.81 SP24. Johns Hopkins University. https://livejohnshopkins.sharepoint.com/
```

############################## ############################## 
# SentimentAnalysis Approach
https://cran.r-project.org/web/packages/SentimentAnalysis/vignettes/SentimentAnalysis.html
############################## ##############################


```{r}
#Get the dictionary
data(DictionaryHE)
data(DictionaryLM)
DictionaryHE

class(DictionaryHE)

```

```{r}
# Apply sentiment dictionary HE
sentiment_dict_result_carbon_corpus = dfm(clean_tokens_cases, 
   dictionary=dictionary(DictionaryHE))
sentiment_dict_result_carbon_corpus
```

```{r}
# Convert it to a data frame
sentiment_dict_result_carbon_corpus_he = convert(sentiment_dict_result_carbon_corpus, to = "data.frame")

# Summarize the sentiment counts
carbon_corpus_summary_he = sentiment_dict_result_carbon_corpus_he %>%
  summarise(
    Positive = sum(positive),
    Negative = sum(negative)
  ) %>%
  pivot_longer(
    cols = c(Positive, Negative),
    names_to = "Sentiment",
    values_to = "Count"
  )
```


```{r}
# Now, use ggplot2 to create a bar plot of sentiment counts
ggplot(carbon_corpus_summary_he, aes(x = Sentiment, y = Count, fill = Sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "Sentiment Analysis using DictionaryHE",
    x = "Sentiment",
    y = "Count"
  )
```


```{r}
# Apply sentiment dictionary LM
dfm(clean_tokens_cases, 
   dictionary=dictionary(DictionaryLM))

```


```{r}
# Convert it to a data frame
sentiment_dict_result_carbon_corpus_lm = convert(dfm(sentiment_dict_result_carbon_corpus, dictionary=dictionary(DictionaryLM)), to = "data.frame")

# Summarize the sentiment counts
carbon_corpu_summary_lm = sentiment_dict_result_carbon_corpus_lm %>%
  summarise(
    Positive = sum(positive),
    Negative = sum(negative)
  ) %>%
  pivot_longer(
    cols = c(Positive, Negative),
    names_to = "Sentiment",
    values_to = "Count"
  )
```


```{r}
ggplot(carbon_corpu_summary_lm, aes(x = Sentiment, y = Count, fill = Sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Sentiment Analysis Summary",
       x = "Sentiment Type",
       y = "Count",
       fill = "Sentiment")
```





####
# Count the Words from the Dictionary I made specifically for Carbon pricing
####
```{r}
#Load custom dictionary
carbon_dictionary = read_csv("~/Desktop/JHU/Semester 2/Text to Data/Module 6/carbon_pricing_terms2.csv", 
                             col_types = cols(Term = col_character())) # Used to remove a warning

class(carbon_dictionary)

```

```{r}
# The column 'Term' contains desired terms
terms_dict = dictionary(list(
  x = carbon_dictionary$Term %>% 
        tolower() %>%  # Convert terms to lowercase
        unique()       # Remove duplicate terms
))

terms_dict
```


```{r}
# Remove stopwords from the tokens
sentiment_dict_result_carbon_corpus_no_stopwords = tokens_remove(clean_tokens_cases, stopwords("en"), padding = FALSE)

```

```{r}
# Apply the dictionary via tokens_lookup to match and aggregate tokens according to the dictionary entries
carbon_corpus_keypol = tokens_lookup(sentiment_dict_result_carbon_corpus_no_stopwords, dictionary = terms_dict, exclusive = FALSE)

```


```{r}
# Create a DFM from the matched tokens
dfm_carbon_corpus_sentiment = dfm(carbon_corpus_keypol)

```


```{r}
# Directly inspect the DFM without reapplying the dictionary
dim(dfm_carbon_corpus_sentiment)

```

```{r}
# Remove the 'x' feature from the DFM
dfm_carbon_corpus_sentiment = dfm_remove(dfm_carbon_corpus_sentiment, "x")
```


```{r}
# Calculate term frequencies
term_counts_corpus_sentiment = textstat_frequency(dfm_carbon_corpus_sentiment)

# Print the term frequency results
print(term_counts_corpus_sentiment)
```

```{r}
# Graph a bar chart with frequency of words
# Top 20 terms by frequency
top_terms = head(term_counts_corpus_sentiment, 20)

# Graph a bar chart with frequency of top 20 words
ggplot(top_terms, aes(x=reorder(feature, -frequency), y=frequency, fill=feature)) +
  geom_bar(stat="identity") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(y = "Frequency", 
       x = "", 
       title = "Top 20 Terms in US Pricing Sentiment Analysis", 
       fill = "Term") +
  guides(fill=FALSE) # Remove the legend
 

#https://cbail.github.io/SICSS_Dictionary-Based_Text_Analysis.html
#Data Viz Fall Semester
```

```{r}


```


```{r}

```



```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```