---
title: "ASSIGNMENT5_WANKELMAN"
output: pdf_document
date: "2024-02-26"
---

```{r}
# Load our dictionaries
install.packages("/Users/my_name/Downloads/topicmodels_0.2-1.tar.gz",repos=NULL,type="source")

```

```{r}
# Load Libaraies
library(quanteda)
library(httr)
library(httr2)
library (qdapDictionaries)
library(jsonlite)
library(ndjson)
library(rjson)
library(dplyr)
library(tidytext)
library(quanteda.textstats)
library(wordcloud2)
library(readtext)
library(tm)
library(jsonview)

```

#Question 1: Setup to deteremine Which Tweets from Nuclear Sentiment dataset mention Japan.
```{r}
# Read Nuclear Sentiment dataset CSV using basic read.csv
# See for additional info: https://quanteda.io/reference/corpus.html
nuclear_data_readcsv = read.csv("~/Desktop/JHU/Semester 2/Text to Data/Module 5/sentiment_nuclear_power _1_.csv",
                            header = TRUE, # We have headers so set to TRUE
                            stringsAsFactor = FALSE) # Make sure the text is retained as char


# Quanteda requires some document name. In case of a CSV or similar format We will assign integers as document IDs.
nuclear_data_readcsv$doc_id = seq.int(nrow(nuclear_data_readcsv))

```


#Question 1:  Which Tweets from Nuclear Sentiment dataset mention Japan.
```{r}
# Sometimes we may have a plural of words por not know specific characters in a word and can use quantifiers/ wildcards

#*: matches at least 0 times.
#+: matches at least 1 times.
#?: matches at most 1 times.
##{n}: matches exactly n times.
#{n, }: matches at least n times.
#{n,m}: matches between n and m times.

grep(pattern = "Jap*", nuclear_data_readcsv$tweet_text, ignore.case = TRUE)

grep(pattern = "Jap*", nuclear_data_readcsv$tweet_text, ignore.case = FALSE)


grep(pattern = "Japa+", nuclear_data_readcsv$tweet_text, ignore.case = TRUE)

grep(pattern = "Japa+", nuclear_data_readcsv$tweet_text, ignore.case = FALSE)
     

#RexEgg. Regex quickstart. Retrieved February 26, 2024, from https://www.rexegg.com/regex-quickstart.html

#RStudio. Regular expressions cheatsheet. Retrieved February 26, 2024, from https://github.com/rstudio/cheatsheets/blob/main/regex.pdf


```

```{r}

#^: matches the start of the string
#$: matches the end os the string
#\b: matches the empty string at either edge of a word. Don't confuse it with ^ $ which marks the edge of a string
#\B: matches the empty string provided it is not at an edge of the word
#\ are characters that need to be escaped with another \.
# A single  \ will match a literal \ character while \\ will be used as RE expression

grep(pattern = "an$", nuclear_data_readcsv$tweet_text, ignore.case = TRUE)

grep(pattern = "an$", nuclear_data_readcsv$tweet_text, ignore.case = FALSE)

#RexEgg. Regex quickstart. Retrieved February 26, 2024, from https://www.rexegg.com/regex-quickstart.html

#RStudio. Regular expressions cheatsheet. Retrieved February 26, 2024, from https://github.com/rstudio/cheatsheets/blob/main/regex.pdf


```

```{r}
# [ 0-9]: matches any digit
# [123]: matches on digits 1,2,3
# [a-z]: matches any lower case letter
# [adTk]: You can also select which characters to match
# [A-Z]: matches any upercase letters
# [A-z]: matches any upper or lowercase letter
#\w: matches any character
#\W: matches any non-character
#\D: matches any non-digit
#\d: matches any digit
#\s: matches any space
#\S: matches any non-space
#\n \r: match newline or carriage return


# There are various wildcards and groupings that can be done with RE

# . : Match any character except newline
# * : Match cahracter(s) multiple times
# [^x]: Don't match given character
# aa | bb: match either aa OR bb
#(): A limited capture group
```

```{r}
#We can combine multiple RE commands in a single expression

# Here we find a string that contains d and with any character after J and a
# but it cannot be followed by any digits using ^.
# Notice that location of ^ matters, before a character negates them
# while following means at the start of a string.

grep(pattern = "(J.a.[^0-9])", nuclear_data_readcsv$tweet_text, ignore.case = TRUE)

grep(pattern = "(J.a.[^0-9])", nuclear_data_readcsv$tweet_text, ignore.case = FALSE)
```

#Question 2:   Remove all occurrences of Twitter usernames (@<username>) and hashtags (#<hashtag>) from the Nuclear Sentiment dataset from Week 3. 

```{r}
print(nuclear_data_readcsv$tweet_text[19])
summary(nuclear_data_readcsv$tweet_text[19])
```


```{r}
# Remove Twitter @username
nuclear_data_cleaned = nuclear_data_readcsv %>%
  mutate(tweet_text = gsub("@\\w+", "", tweet_text))

# Remove hashtags
nuclear_data_cleaned = nuclear_data_cleaned %>%
  mutate(tweet_text = gsub("#[[:alnum:]_]+", "", tweet_text))
```


```{r}
# Print the tweet text of the 19th entry to check for @ and #
print(nuclear_data_cleaned$tweet_text[19])
```

```{r}
# Assign document IDs - Assigning unique document IDs to each text entry is an important step before creating a corpus. Document IDs serve several purposes: Identification, Order Preservation, Analysis.
nuclear_data_cleaned$doc_id = seq_along(nuclear_data_cleaned$tweet_text)

#Feinerer, I., & Hornik, K. (n.d.). Text Mining Package 'tm'. Retrieved [Date you accessed the document], from https://cran.r-project.org/web/packages/tm/tm.pdf

#Stack Overflow user. (2013, February 13). How can I manually set the document ID in a corpus? Stack Overflow. https://stackoverflow.com/questions/14852357/how-can-i-manually-set-the-document-id-in-a-corpus

#Benoit, K., & others. Corpus. quanteda. Retrieved 2024, Feburary 27, from https://quanteda.io/reference/corpus.html

#OpenAI. "Importance of Assigning Document IDs in Corpus Creation in R." Response to Query on Text Analysis with R. Received 2024, Feburary 26. ChatGPT Session.
```


```{r}
# Create a corpus from Regex cleaned data
cleaned_corpus = corpus(nuclear_data_cleaned, text_field = "tweet_text")

```

```{r}
summary(cleaned_corpus)

summary(cleaned_corpus[19])

```

#Question 3: Remove the (fake and inserted by your instructor) social security numbers in the Amazon Musical Instruments JSON ATTACHED TO THIS WEEK'S HOMEWORK.
```{r}
library(stringr)

ndjson_review = ndjson::stream_in('/Users/jcw81/Desktop/JHU/Semester 2/Text to Data/Module 5/Musical_Instruments_5_SSN.json')
ndjson_review

# Basic subsetting guide: https://www.statmethods.net/management/subset.html
```

```{r}
# Define a regex pattern (both XXX-XX-XXXX and XXX-XXX-XXXX patterns)
ssn_pattern = "^(?!666|000|9\\d{2})\\d{3}-(?!00)\\d{2,3}-(?!0{4})\\d{4}$" #found this in Geeksforgeeks reference

#GeeksforGeeks. How to Validate SSN (Social Security Number) Using Regular Expression. Retrieved 2024, Feburary 25, from https://www.geeksforgeeks.org/how-to-validate-ssn-social-security-number-using-regular-expression/

#LearningDS. Text Data and Regular Expressions. Retrieved 2024, Feburary 26, from https://learningds.org/ch/13/text_regex.html

#Goyvaerts, J., & Levithan, S. (2012). Regular Expressions Cookbook. O'Reilly Media. Retrieved 2024, Feburary 26, from https://learning.oreilly.com/library/view/regular-expressions-cookbook/9781449327453/ch04s12.html#validation-ssn-discussion
```

```{r}
#Found this on GeeksforGeeks and thought I would try it in R to test if my ssn_pattern actually worked beofre applying it to Musical_instuments_5_SSN.json
# Function to validate the SSN (Social Security Number)
isValidSSN = function(str) {
  
  # If the SSN (Social Security Number) is empty return FALSE
  if (str == "") {
    return(FALSE)
  }
  
  # Return TRUE if the SSN (Social Security Number) matches the Regex
  if (str_detect(str, regex(ssn_pattern, ignore_case = TRUE))) {
    return(TRUE)
  } else {
    return(FALSE)
  }
}

# Driver Code
# Test Case 1:
str1 = "856-45-6789"
print(isValidSSN(str1))

# Test Case 2:
str2 = "000-45-6789"
print(isValidSSN(str2))

# Test Case 3:
str3 = "856-452-6789"
print(isValidSSN(str3))

# Test Case 4:
str4 = "856-45-0000"
print(isValidSSN(str4))

#GeeksforGeeks. (n.d.). How to Validate SSN (Social Security Number) Using Regular Expression. Retrieved [date you accessed the resource], from https://www.geeksforgeeks.org/how-to-validate-ssn-social-security-number-using-regular-expression/

```

```{r}
# Replace SSNs in the reviewText field with "REMOVED" to indicate SSN's that have been identified and removed
ndjson_review$reviewText = sapply(ndjson_review$reviewText, function(text) {
  str_replace_all(text, ssn_pattern, "REMOVED")
})

```

